\documentclass[ALICE,manyauthors]{ALICE_analysis_notes}
%
\input{commands.tex}
\usepackage{rotating}
\usepackage{float}
\usepackage{listings}
\usepackage{multirow}
%\usepackage{subcaption}
\usepackage[ampersand]{easylist}
\usepackage{hyperref}
\usepackage{comment}
\usepackage{bm}
\usepackage{subcaption}
\usepackage[section]{placeins}
\usepackage{color}
\usepackage[toc,page]{appendix}
%
\begin{document}%
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{titlepage}
%
\PHnumber{ALICE-ANA-2018-xxx} 
\PHdate{\today}
%
%%% Put your own title + short title here:
\title{D mesons in jets in \pPb\ collisions: preliminary figures for QM 2018}
\ShortTitle{D-jets in \pPb\ collisions: preliminary figures for QM 2018}   % appears on right page headers
%%% BASED ON THE QM2017 ANALYSIS NOTE ..... %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\author{Salvatore Aiola$^{1}$, Fabio F. Colamaria$^{2}$, Andrea Rossi$^{3}$, Antonio C. O. da Silva$^{4,5}$, Barbara A. Trzeciak$^{4}$\\
$D^{0}$-jets: Auro Mohanty$^{4}$, Barbara A. Trzeciak$^{4}$}
\author{
1. Yale University, USA\\
2. University of Bari and INFN, Italy\\
3. University of Padova and INFN, Italy\\
4. Utrecht University, the Netherlands\\
5. University of S\~ao Paulo, Brazil\\
}
\author{Email: barbara.antonina.trzeciak@cern.ch}
%
\ShortAuthor{ALICE Analysis Note 2018}      % appears on left page headers, do not change
%
\begin{abstract}
The study of the charm content of jets is interesting because up to now
it has eluded a precise quantitative understanding in the framework of perturbative QCD (pQCD).
The charm content of jets is known to arise both from prompt production in the process ${\rm gg\, (q\bar{q})} \rightarrow {\rm c\bar{c}}$, and
from the parton shower of gluons and light-flavor quarks.
Charm hadrons coming from the fragmentation of prompt charm jets 
are expected to carry a larger fraction of the total jet momentum,
as compared to those where the charm content arises later in the
parton shower. Therefore the measurement of charm jet fragmentation functions (FFs) 
can be used to estimate the relative strength of the two mechanisms.
Heavy-flavor jets can also provide important insights into the Quark-Gluon Plasma (QGP)
produced in ultra-relativistic heavy-ion collisions, as heavy quarks are predicted
to interact with the QGP differently compared to light quarks and gluons. 
The aim of the analysis is to extract both the $p_{\rm T}$ spectrum of the D-tagged jets in p-Pb collisions at \snn\ = 5.02 TeV. 
We identify D-meson candidates via their hadronic decay channels using topological selections and particle identification. These 
candidates are combined with the other charged tracks reconstructed by the central tracking system, using the anti-$k_T$ jet-finding algorithm. 
We extract the yield of D-tagged jets through their invariant mass analysis in bins of D $p_T$ and get their jet $p_T$ spectra.  \\
Aim of this note is to present details of the \Dzero-tagged jet analysis to be approved as a preliminary result for the Quark Matter 2018 conference, and it updates the previous preliminary result on the \Dstar-tagged jets \pt\ differential cross-section in \pPb at \snn = 5.02 TeV.
\end{abstract}
\end{titlepage}
%
\tableofcontents
%\newpage
\input{content.tex}               %%%%%%%%%%% put the body of the article here

%%%%%% Appendices %%%%%%%%%%%%%%
\newpage
\begin{appendices}
\input{SysPbPbbinning}
\end{appendices}
%


\end{document}
